Using HMMs for pre-snap coverage detection

### 2024-11-22 submission.Rmd
text

#### 2. HMM Analysis
We model the movements of defensive players during the phase of pre-snap motion within a hidden Markov framework, in which the underlying states represent the offensive players to be guarded (see Franks et al., 2015 for a similar approach in basketball).

>>>>

#### 2. HMM Analysis
We model the movements of defensive players during the phase of pre-snap motion within a hidden Markov framework, in which the underlying states represent the offensive players to be guarded (see Franks et al., 2015 for a similar approach in basketball). In contrast to Groom et al., 2024, who enforce a state to proxy zone coverage during corner kicks in soccer, we cannot do that as the classical zones in American football will only be covered post-snap. To remidiate this problem, we aim to derive the decision of man- or zone coverage from the number of switches for individual players. In particular, a low number of switches when offensive players are in motion indicates man coverage whereas a higher number indicates zone coverage.
